bplist00?_WebMainResource?	
_WebResourceMIMEType_WebResourceTextEncodingName_WebResourceFrameName^WebResourceURL_WebResourceDataZtext/plainUUTF-8P_@http://www2.stat.duke.edu/~cr173/Sta112_Fa16/files/gapminder.RmdO?<html><head><style id="style-1-cropbar-clipper">/* Copyright 2014 Evernote Corporation. All rights reserved. */
.en-markup-crop-options {
    top: 18px !important;
    left: 50% !important;
    margin-left: -100px !important;
    width: 200px !important;
    border: 2px rgba(255,255,255,.38) solid !important;
    border-radius: 4px !important;
}

.en-markup-crop-options div div:first-of-type {
    margin-left: 0px !important;
}
</style></head><body><pre style="word-wrap: break-word; white-space: pre-wrap;">
---
title: "Gapminder Analysis"
author: "b"lablba
date: "8/30/2016"
output: html_document
---

## Exercise 0

### Load packages

Load the following packages for 

- data wrangling (`dplyr`), and 
- data visualizaiton (`ggplot2`)

```{r load_pkgs, message=FALSE}
library(dplyr)
library(ggplot2)
```

### Load data

```{r load_data}
gap = read.csv("https://bit.ly/gap_data_upd")
```

## Exercise 1

Visualize the relationship between life expectancy and population in 1952 using a scatter plot.

```{r ex1}
gap01 = filter(gap, year == 1952)
ggplot(gap01, aes(x = lifeExp, y = pop)) + geom_point()
```


### Exercise 2

Visualize the relationship between life expectancy and GDP per capita in 2007 using a scatter plot and color the points by continent.

```{r ex2}
ggplot(gap01, aes(x = lifeExp, y = pop, color = continent, size = gdpPercap)) + geom_point()
```